Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
I don't think this adds anything, does it?

For higher-order contracts, the notion has two facets. A \nickel{Num -> Str}
contract can be violated in two ways: by the function returning a value that is
not a string, or by the caller providing an argument that is not a number.  The
former is embodied by the same notion as before: $f \in \llbracket Num \to Str
\rrbracket^+$ if whenever $f$ receives a number, it returns a string.  One
important contribution of~\cite{KeilThiemannUnionIntersection}, upon
which~\cite{RootCauseOfBlame} builds upon, is to extend the notion of contract
satisfaction to \emph{contexts} (i.e. a continuations), embodying the caller's
obligations. A context $K$ is a term with a hole to be filled with a term (see
Figure~\ref{fig:valid-contexts} for examples). Then, $K \in \llbracket Num \to
Str \rrbracket^-$ (the context $K$ satisfies the contract \nickel{Num -> Str})
if it only applies the hole to arguments satisfying the \nickel{Num} contract.

>>>>

For higher-order contracts, the notion has two facets. A \nickel{Num -> Str}
contract can be violated in two ways: by the function returning a value that is
not a string, or by the caller providing an argument that is not a number.  The
former is embodied by the same notion as before: $f \in \llbracket Num \to Str
\rrbracket^+$ if whenever $f$ receives a number, it returns a string.  One
important contribution of~\cite{KeilThiemannUnionIntersection}, upon
which~\cite{RootCauseOfBlame} builds upon, is to extend the notion of contract
satisfaction to \emph{contexts}, embodying the caller's
obligations. A context $K$ is a term with a hole to be filled with a term (see
Figure~\ref{fig:valid-contexts} for examples). Then, $K \in \llbracket Num \to
Str \rrbracket^-$ (the context $K$ satisfies the contract \nickel{Num -> Str})
if it only applies the hole to arguments satisfying the \nickel{Num} contract.
